Improving the Replicability of Psychological Science Through Pedagogy

### 2017-07-23 paper/paper.Rmd
Combine subject pool & sample size; discuss cost

### Subject population

We chose to use Amazon Mechanical Turk (AMT) as a platform for our replication studies. We used AMT to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge. As much of psychological research is now conducted online, an additional pedagogical benefit of conducting online replications is to build competence in these skills. Even if students’ current research does not use AMT, these replications allow students to build a skillset that can be used throughout their academic careers. Other classes many find using university participant pools or recruitment of community samples more feasible and appropriate.

### Workflow tools

All our studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser. All analyses were written using R, a free and open-source platform for statistical analysis.  Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables. This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document. This method of writing allows students to share a single compiled document with instructors via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.].

@@

### Sample size and power analyses

Determining appropriate sample sizes is a major challenge in replication research [@button2013;@simonsohn2015]. Sample planning based on analysis of the achieved effect size in a previously-published study is problematic because of the likelihood of inflation of published effect sizes due to the "winner's curse" [@hoenig2001;@button2013]. But -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases. For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for studies that were initially large and/or adequately powered. Samples for course projects will be limited by the available resources, but for replication research of the type advocated here, achieving high power for a smaller number of studies is preferable to conducting more lower-power studies: Results are much more likely to be to be interpretable by students and to make a contribution to the replication literature. Regardless of the eventual sample collected, we find that the discussion of sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in this planning process.

>>>>

### Subject population and sample size

For pedagogical replications to also make a *scientific* contribution, they must be adequately powered and use subject populations comparable to those used in typical lab research. With these needs in mind, we chose to use Amazon Mechanical Turk (AMT) for our replication studies. AMT facilitates the process of recruiting diverse, high-quality samples [@BuhrmesterKwangGosling11;@CrumpEtAl13_Turk] that are large enough to enable replications of between-subjects designs (which typically require large samples). Because psychological research is increasingly conducted online, an additional pedagogical benefit is to build competence in these skills. Even if students’ current research does not use AMT, these replications allow students to build a skillset that can be used throughout their academic careers.

Still, collecting sufficiently large samples through AMT may strain financial resources. Depending on the number of target studies, the needs of those studies, the level of the student group, and the total funds allocated to the course (e.g. through teaching grants or departmental support), other populations may be more feasible and appropriate. For instance, recruitment from community samples or university participant pools may provide high-quality data while reducing costs and eliminating a major technical component of the workflow.

Cost considerations also enter decisions about determining appropriate sample sizes, a major challenge in replication research [@button2013;@simonsohn2015]. Sample planning based on analysis of the achieved effect size in a previously-published study is problematic because of the likelihood of inflation of published effect sizes due to the "winner's curse" [@hoenig2001;@button2013]. But it may not be feasible to follow more conservative guidelines in all cases. For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies, but be unnecessary for studies that were initially large and/or adequately powered.

As a rule of thumb, for the type of replication research advocated here, conducting a small number of high-powered studies using representative samples is preferable to conducting a large number of under-powered studies in convenience samples: Results are much more likely to be to be interpretable by students and to make a contribution to the replication literature. Regardless of the eventual sample collected, we find that the discussion of subject population & sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in this planning process.

<!-- as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge. -->
### Workflow tools

All our studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser. All analyses were written using R, a free and open-source platform for statistical analysis.  Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables. This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of a single unified document that would become their final report. This method of writing allows students to easily share their cumulative work to date with instructors via a hyperlink, facilitating review of exposition, results, and code together in one location^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.].

@@
